%realize  LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{url}
\usepackage{enumitem}
\setlength{\textheight}{10in} % increase text height to fit on 1-page

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tgbonum}


\begin{document}
\name{JINYANG YAO\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name

\address{\textbf{Email:} jimmy123good@hotmail.com \\
        \textbf{Github: }https://github.com/ailrk \\
         \textbf{Blog:}    https://ailrk.github.io/home \\
         \textbf{Contact:}  (250) 899 2600}
\begin{resume}

\section{EDUCATION}
The University of British Columbia, Kelowna, BC, Canada  \hspace{1.2in} \textbf{2017-Present}\\
    Currently a fourth year undergraduate student. Honours in Computer Science, minor in Mathematics \\

\section{PAST EXPERIENCES}
\begin{itemize}[leftmargin=-.1in]
    \item \textbf{2019 Summer:} Chongqing University HVAC department
        \vspace{0.05in}\\ Participated the ``Yangzi River area air conditioning and heating solution and its corresponding systems'' research project. Developed a program to select building designs that satisfies certain multi-objective constraints. \\
     Designed and implemented the project's web platform with flask and react. \\
    \item \textbf{2020 -2021: } UBC computer science honor program. \\
        \vspace{0.05in} Using semi-supervised learning to assess programming assignments. Developed a method allows human intervention to guide the algorithm to improve the clustering result. \\


\end{itemize}

\vspace{-0.2in}
\section{PERSONAL PROJECTS}

    \vspace{-0.1in}
    \begin{tabbing}
        \hspace{2.4in}\= \hspace{0.9in}\= \kill
        {\bf cppparsec } \>               \>\url{github.com/ailrk/cppparsec}\\

    \end{tabbing}\vspace{-30pt}
    A C++ monadic parser combinator inspired by Haskell's parsec library.

    \vspace{-0.2in}
    \begin{tabbing}
        \hspace{2.4in}\= \hspace{0.9in}\= \kill
        {\bf mstl } \>               \>\url{github.com/ailrk/markdowndb.macro}\\
    \end{tabbing}\vspace{-30pt}
    A partial replication of the C++ STL, referenced multiple implementations and added some meta programming facilities.

    \vspace{-0.2in}
    \begin{tabbing}
        \hspace{2.4in}\= \hspace{0.9in}\= \kill
        {\bf lambda cube} \>               \>\url{github.com/ailrk/lambda-cube}\\

    \end{tabbing}\vspace{-30pt}
    A set of langauges extended from the simply typed lambda calculus.

    \vspace{-0.2in}
    \begin{tabbing}
        \hspace{2.4in}\= \hspace{0.9in}\= \kill
        {\bf pogger } \>               \>\url{github.com/ailrk/pogger}\\

    \end{tabbing}\vspace{-30pt}
    A partially R5S5 compliant scheme implementation in Haskell.

    \vspace{-0.2in}
    \begin{tabbing}
        \hspace{2.4in}\= \hspace{0.9in}\= \kill
        {\bf canvas-bot} \>               \>\url{github.com/ailrk/canvas-bot}\\

    \end{tabbing}\vspace{-30pt}
    A command line client for canvas in Typescript.

\section{SKILLS}
    \begin{itemize}[leftmargin=-.2in]
        \setlength\itemsep{-1em}
        \item \textbf{Programming Language:} Mostly used: Haskell, C++, Python, Typescript. Familiar with: SML, Ocaml, Common lisp, Java. \\
        \item \textbf{Python: 4 years}
          Experienced with flask web framework and sqlalchemy database ORM.
          Familiar with traditional machine learning algorihtms and implement models with sklearn.
          Familiar with python concurrency model and meta programming technics. \\
        \item \textbf{C++: 3 years}
          Familiar with the C++ data model, template meta programming,
          generic programming and the implementation of the STL. \\
        \item \textbf{Haskell 2 years}
          Familiar with functional programming.
          Understand GHC compilation process and some GHC optimizations.
          Familiar with type level programming.\\
        \item \textbf{Typescript: 2 years:} Understand the structural typing system and some type level techniques. Familiar with V8 optimization, libuv and event loop system. Understand reactor pattern. Experienced with React and nodeJS. \\
        \item \textbf{Type theory:} Implemented languages on Lambda Cube. \\
        \item \textbf{Math:} Minor in Mathematics. Linear Programming, Dynamic system, Number Theory, Abstract Algebra and some applications \\
        \item \textbf{Language:} Have been living in \textbf{English} Speaking country for more than 3 years, received band 7 for IELTS in 2017. Native \textbf{Chinese} speaker. Learning \textbf{Japanese}.
    \end{itemize}

\end{resume}
\end{document}
